Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-11 paper.Rnw
fixed typo in code

# Load the bullet matching training data and make some adjustments:
#   1. filter out observations known to have tank rash
#   2. exclude features not used to train the rtrees random forest 
#   3. add a case variable
#   4. change the name of the same_source variable to match the test data
#   5. reorder the variables
bullet_train <- readr::read_csv("data/bullet-train.csv.zip") %>%

# Load the bullet test data
bullet_test <- readr::read_csv("data/bullet-test.csv.zip")

>>>>

# Load the bullet matching training and testing data
bullet_train <- readr::read_csv("data/bullet-train.csv.zip")
bullet_test <- readr::read_csv("data/bullet-test.csv.zip")
